---
title: "p8105_hw1_cr3442"
author: "Cheng Rao"
date: "2024-09-21"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

The purpose of this file is to finish p8105 homework 1 and test if I can submit the .Rmd successfully to the Github as I am just a beginner in R. This assignment will try to be consistent in format with a solution in Lecture 'Writing with data'. Now let me first deal with Problem 1.

# Problem 1

First we download a package containing the penguins dataset.

```{r install_package, eval=FALSE}
install.packages("palmerpenguins")
```

then we load the penguins dataset.

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

Next we use inline R code to describe the data in this dataset, by using summary() and str(). At first summary().

```{r penguins summary}
penguins_summary <- summary(penguins)
```

Next str().

```{r peguins structure}
structure_penguins <- str(penguins)
```

The we describe the size of the dataset (using nrow and ncol).

```{r size}
# The size of the dataset (using nrow and ncol)
number_rows <- nrow(penguins)
number_cols <- ncol(penguins)
```

Then we calculate the mean of flipper length.

```{r mean of flipper length}
# The mean flipper length, ignoring missing value and calculate the mean
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Next we make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x).

```{r scatterplot}
library(ggplot2)

# Make a scatterplot and the color points is using the species variable inside of aes, Use na.rm = TRUE to ignore missing values
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
 
   geom_point(na.rm = TRUE) +
  
  labs(title = "Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)", x = "bill_length(mm)", y = "flipper_length(mm)") 
```

Now Problem 1 is finshed already and I want to summit it to the Github.


# Problem 2

I to need create a data frame containing four different types of variables and find the means of these variables. Finally, I need to try to use as.numeric to force conversion of three of the variables.

First let's create the data frame.

```{r create_dataframe}

# Use knitr package for better table formatting
library(knitr)

# Create a data frame containing four different types of variables
df <- data.frame(
  
  numeric_sample = rnorm(10),  # A random sample of size 10 from a standard Normal distribution
 
  logical_vector = rnorm(10) > 0,  # A logical vector indicating whether elements of the sample are greater than 0
  
  character_vector = letters[1:10],  # A character vector of length 10
  
  factor_vector = factor(rep(c("Level 1", "Level 2", "Level 3"), length.out = 10))  # A factor vector of length 10, with 3 different factor “levels”

  )

# Show the data frame using kable
kable(df)
```

Next I am going to calculate the means of these variables, the tidyverse is already loading and I will use the pull function.

```{r calculate_means}
# Calculate the means of these variables,using mean(df)
mean_numeric <- mean(pull(df, numeric_sample))
mean_logical <- mean(pull(df, logical_vector))

# The two variables cannot be directly averaged, so try() is used, and silent = TRUE is used to suppress the printing of error messages
mean_character <- try(mean(pull(df, character_vector)), silent = TRUE)
mean_factor <- try(mean(pull(df, factor_vector)), silent = TRUE)

# Print the results
mean_numeric
mean_logical
mean_character
mean_factor
```

The results show that the meaning of numeric and logical works and the meaning of character and factor doesn’t work.

Then I write a code chunk that applies the as.numeric function to the logical, character, and factor variables and try to coerce them to numeric, so I use numeric_xxx to represent these variables.

```{r coerce}
# coerce variables to numeric
numeric_logical <- as.numeric(df$logical_vector)
numeric_character <- as.numeric(df$character_vector)
numeric_factor <- as.numeric(df$factor_vector)
```
 
 At last the problem 2 is done and hence the homework 1 is finished. I hope I make fewer mistakes. 
