---
title: "p8105_hw1_cr3442"
author: "Cheng Rao"
date: "2024-09-21"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

The purpose of this file is to finish p8105 homework 1 and test if I can submit the .Rmd successfully to the Github as I am just a beginner in R. This assignment will try to be consistent in format with a solution in Lecture 'Writing with data'. Now let me first deal with Problem 1.

# Problem 1

First we download a package containing the penguins dataset.

```{r install_package, eval=FALSE}
install.packages("palmerpenguins")
```

then we load the penguins dataset.

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

Next we use inline R code to describe the data in this dataset, by using summary() and str(). At first summary().

```{r penguins summary}
penguins_summary <- summary(penguins)
```

Next str().

```{r peguins structure}
structure_penguins <- str(penguins)
```

The we describe the size of the dataset (using nrow and ncol).

```{r size}
# the size of the dataset (using nrow and ncol)
number_rows <- nrow(penguins)
number_cols <- ncol(penguins)
```

Then we calculate the mean of flipper length.

```{r mean of flipper length}
# the mean flipper length, ignoring missing value and calculate the mean
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Next we make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x).

```{r scatterplot}
library(ggplot2)

# make a scatterplot and the color points is using the species variable inside of aes, Use na.rm = TRUE to ignore missing values
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(na.rm = TRUE) +
  labs(title = "Scatterplot of flipper_length_mm (y) vs bill_length_mm (x)", x = "bill_length(mm)", y = "flipper_length(mm)") 
```

Now Problem 1 is finshed already and I want to summit it to the Github.



